Parks Data

### 2020-04-20 02_parks_data.Rmd
Updates to build site
Fix problem with B527\r\nB527 parknum

In this document we get the parks data from the New York City open data
repository and do some cleaning. First, we get the parks dataset. The original
data dictionary is available at 
[on Github](https://github.com/CityOfNewYork/nyc-planimetrics/blob/master/Capture_Rules.md#open-space)
```{r parks}
parks_url <- "https://data.cityofnewyork.us/api/geospatial/y6ja-fw4f?method=export&format=GeoJSON"
parks <- st_read(parks_url, stringsAsFactors = FALSE) %>%
  mutate(shape_area = as.numeric(shape_area))
```

@@

Now we write out the data for the future.
```{r write}
write_rds(open_spaces, "data/open_spaces.rds")
geojsonio::geojson_write(open_spaces, file = "data/open_spaces.geojson")
```

>>>>

In this document we get the parks data from the New York City open data
repository and do some cleaning. First, we get the parks dataset. The original
data dictionary is available at 
[on Github](https://github.com/CityOfNewYork/nyc-planimetrics/blob/master/Capture_Rules.md#open-space)
```{r parks}
parks_url <- "https://data.cityofnewyork.us/api/geospatial/y6ja-fw4f?method=export&format=GeoJSON"
parks <- st_read(parks_url, stringsAsFactors = FALSE) %>%
  mutate(
    shape_area = as.numeric(shape_area),
    parknum = ifelse(parknum == "B527\r\nB527", "B527", parknum) 
  ) 
```

@@

Now we write out the data for the future.
```{r writefiles}
write_rds(open_spaces, "data/open_spaces.rds")
geojsonio::geojson_write(open_spaces, file = "data/open_spaces.geojson")
```
